Pillar 2 - Topic Modeling

### 2019-03-19 Pillar 2 - Topic Modeling.Rmd
deleting redundant code

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
##Functions for models (get gamma, get beta, extract_dtm)
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(wt) d_cast[[wt]]

# #get beta
# get_beta <- function(results){
#   
#   tidy(results, matrix = "beta")           %>%
#     mutate(topic = paste("Topic", topic) ) %>%
#       arrange(topic, desc(beta) )
#   
# }
# 
# #get gamma
# get_gamma <- function(results){
#   
#   tidy(results, matrix = "gamma")          %>%
#     mutate(topic = paste("Topic", topic) ) %>%
#       arrange(topic, desc(gamma) )
# }

get_distributions <- function(model, distrib_str){ #input gamma or beta
  tidy(model, matrix = distrib_str)        %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(!!sym(distrib_str)))
}

#perplexity Function
my_perplexity <- function(model, d_cast){
  perplexity(model, d_cast, estimate_theta = FALSE)
}

my_logLik <-  function (model)

@@

```
#DELETE LATERRRRRR- HELPER IMPORT
```{r}
load("Output/topic_model.RDATA")
```

##Model Evaluation
###Plots
```{r perplexity plots, eval = TRUE}
#plot evaluation
plot_evaluation <- function(){

@@

plot_evaluation()
```

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
##Saving filed for different sessions
For internal use:
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" )
```
For different sessions:
```{r saving, eval = TRUE}
save(topic_model_gb, 
     file = "Output/topic_model_gb.RDATA")
```
#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

>>>>

We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`
##Functions for models (get gamma, get beta, extract_dtm)
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

#extract Distributions (Gamma/Beta)
get_distributions <- function(model, distrib_str){ #input gamma or beta
  tidy(model, matrix = distrib_str)        %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(!!sym(distrib_str)))
}

#perplexity Function
my_perplexity <- function(model, dtm){
  perplexity(model, dtm, estimate_theta = FALSE)
}

@@

#View(test_topic_model)
test_topic_model
```
#DELETE LATERRRRRR- HELPER IMPORT
```{r}
load("Output/topic_model.RDATA")
```

##Model Evaluation
###Plots
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(){

@@

#Plot
plot_evaluation()
```

##Saving filed for different sessions
For internal use:
```{r}
# save(topic_model, file = "Output/topic_model.RDATA" )
```

#Distributions
#NOTE: We need to select how many topics to use
##Distributions of best models
```{r Distributions, eval = FALSE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40
